\ZZnonchapter{odd}{PUBLICATIONS}{y}{0pt}
\ix{publication environment//publications environment}
\index{\verb+\begin{publicationa}+@\verb+\begin{publication}+}
\index{\verb+\begin{publications}+}

\noindent\textbf{Journal Publications}
\begin{itemize}
        \item[$\lrb{1}$] Charla, S., Meckl, P. , Yao, B. Modelling and Parameter Estimation of Diesel Engine
        Aftertreatment System under Catalyst Saturation for Aging Diagnostics. (In preparation for submission to Journal
        of Dynamic Systems, Measurement, and Control).
        %==============================
        \item[$\lrb{2}$] Charla, S., Meckl, P. , Yao, B. Discrete Nonlinear Modelling and Parameter Estimation
        for Diesel Engine SCR System Diagnostics. (In preparation for submission to Journal of Dynamic Systems,
        Measurement, and Control).
        %==============================
\end{itemize}

\noindent\textbf{Conference Publications}
\begin{itemize}
        \item[$\lrb{1}$] Charla, S., Meckl, P. , Yao, B. (2024). Reduced Order Linear Modelling and Identification for Diesel Engine SCR-ASC System Diagnostics. IFAC-PapersOnLine, 58(28), 168-173.
        %==============================
        \item[$\lrb{2}$] Charla, S., Yao, B., Voyles, R. (2024). Uncertainty rejection in multirotor motor-propeller actuators using rpm feedback. IFAC-PapersOnLine, 58(28), 534-539.
        %==============================
        \item[$\lrb{3}$] Charla, S., Yao, B., Voyles, R. (2024). Identification of multirotor actuator dynamics with rpm feedback for improved control. In 2024 American Control Conference (ACC) (pp. 427-432). IEEE.
        %==============================
        \item[$\lrb{4}$] Charla, S. , Yao, B., Voyles, R. (2022). On enhancing the bandwidth of the actuator dynamics in a multi-rotor aerial vehicle. IFAC-PapersOnLine, 55(37), 536-541.
\end{itemize}
