\section{Parameter Estimation and Aging Detection in Test Cell Data}
Using the parameter estimation approach outlined in the previous section, we analyze the test cell data to estimate the
parameters of the saturated catalyst model. The parameter estimates using FTIR measurements from the test cell
experiments are tabulated in Table-\ref{tab::parm_FTIR}. The parameters show consistency across repeated RMC (Ramped
Mode Cycle) and Hot-FTP (Federal Test Procedure) tests on the same catalyst validating the estimation approach. However,
the parameters vary significantly between RMC and Hot-FTP tests. This is predominantly due to the differences in the
temperature ranges experienced by the catalyst during the tests, which affects the Arrhenius temperature dependence of
the rate constant and the concentration of viable voids on the catalyst surface. The temperature range of the data
considered during the RMC tests is between 240째C and 360째C, while for the Hot-FTP tests it is between 200째C and 300째C.
\begin{table}[ht]
        \centering
        \caption{Parameter Estimates using FTIR Data}
        \label{tab::parm_FTIR}
        \begin{tabular}{l c c c c}
                \hline \hline
                Test & $\hat \theta_1 $ & $\hat \theta_2 $ & $\hat \theta_3 $ & $\sigma$\\ \hline \hline
                        DG RMC 1  & -0.63 & 0.55 & 38.74 & 1.14\\
                        DG RMC 2  & -0.82 & 0.69 & 38.61 & 1.08\\
                        DG RMC 3  & -0.80 & 1.12 & 38.78 & 1.10\\
                        Aged RMC  & -1.31 & 1.89 & 36.94 & 1.01\\ \hline
                        DG Hot FTP 1 & -2.14 & -5.80 & 39.53 & 1.35\\
                        DG Hot FTP 2 & -3.45 & -7.99 & 38.05 & 1.30\\
                        DG Hot FTP 3 & -3.37 & -6.42 & 38.88 & 1.33\\
                        Aged Hot FTP & -4.54 & -8.01 & 37.00 & 1.31\\
                \hline\hline
        \end{tabular}
\end{table}
% ======================================================================================================================
The parameter estimates using $NO_x$ sensor measurements from the test-cell experiments are tabulated in
Table-\ref{tab::parm_nox}. The parameter estimates are different from those obtained using FTIR measurements
(Table-\ref{tab::parm_FTIR}) due to the cross-sensitivity of the $NO_x$ sensor to ammonia. However, the parameters show
consistency across repeated tests on the same catalyst under similar test conditions. The $NO_x$ sensor cross-
sensitivity error $\varepsilon_{\chi}(T)$ introduces bias in the parameter estimates as part of the error that has the
same temperature dependence as the model structure enters into the parameter estimates. Thus, the linear programming problem estimated the parameters with an added bias term as shown below:
\begin{align}
    \varepsilon_{\chi}(T) &= \phi_{sat}(T(k))^T \theta_{\varepsilon_{\chi}} + \epsilon_{\chi}\\
    J(\theta_{sat})
                    &= \sum_{k=0}^{N-1} \lr{ \phi^T(k) \lr{\theta_{sat} + \theta_{\varepsilon_{\chi}}} - \eta (k) }
\end{align}
Thus, the estimated parameters using $NO_x$ sensor measurements will have a bias dependent on the cross-sensitivity
error characteristics of the sensor used. From, the experimental results, it is observed that $NO_x$ sensor
cross-sensitivity reduces the difference between the estimates of aging-factor
(Figure~\ref{fig::alpha_sat_ssd}, \ref{fig::alpha_sat_iod}) between aged and degreened catalysts. But the overall trend
of change in parameter values remains consistent.
%===
\begin{table}[ht]
        \centering
        \caption{Parameter Estimates using $NO_x$ Sensor Data}
        \label{tab::parm_nox}
        \begin{tabular}{l c c c c}
                \hline \hline
                Test & $\hat \theta_1 $ & $\hat \theta_2 $ & $\hat \theta_3 $ & $\sigma$ \\ \hline \hline
                        DG RMC 1 & -0.70 & 0.56 & 38.48 & 1.10\\
                        DG RMC 2 & -1.18 & 0.93 & 38.43 & 1.07\\
                        DG RMC 3 & -0.54 & 0.62 & 38.99 & 1.06\\
                        Aged RMC & -1.03 & 1.26 & 37.80 & 1.00\\ \hline
                        DG Hot FTP 1 & -2.30 & -6.11 & 37.08 & 1.28\\
                        DG Hot FTP 2 & -2.71 & -6.13 & 36.22 & 1.27\\
                        DG Hot FTP 3 & -3.92 & -6.17 & 35.81 & 1.30\\
                        Aged Hot FTP & -6.42 & -13.06 & 34.73 & 1.34\\
                \hline\hline
        \end{tabular}
\end{table}
%==
% ==================================================================================================================
Furthermore, the above delineated parameter estimation method has a limitation that the dataset must have response
of the catalyst under saturation for finite duration. If this condition is not met, the algorithm estimates the
parameters considering the maximum concentration of adsorbed ammonia as the concentration corresponding to catalyst
saturation (Appendix-\ref{sec::necessary_cond}).
% ==================================================================================================================
\input{secs/5-sat_detect/3_subs/0_necc_cond.tex}
\input{secs/5-sat_detect/3_subs/1_cat_mode.tex}
\input{secs/5-sat_detect/3_subs/2_aging_detection.tex}
