\section{Remarks on Detector Performance}

The study introduces a parameter estimation-based hypothesis testing algorithm for catalyst aging detection, based on
the hypothesis that model parameters associated with catalyst storage capacity change with aging
\cite{daya2018development} and \cite{daya2020kinetic}. The hypothesis testing framework requires not only the parameter
estimates but also their distributions. To address this, the maximum likelihood estimation (MLE) framework and its
asymptotic properties are employed. The linear programming problem (\ref{eqn::lin_prog}) for estimating the parameters
of the saturated model is demonstrated to be equivalent to MLE under a half-normal distribution of the model-structure
error between the actual system response and the saturated model prediction. For the unsaturated model, the
least-squares problem corresponds to MLE under the Gaussian distribution of the model-structure error. Utilizing the
parameter distributions, a Wald test-based detector (\ref{eqn::wald_statistic}) is proposed to quantify the distance
between the estimated parameters and the known degreened parameters, scaled by the Fisher information of the parameter
estimate distribution. The influence of nuisance parameters is also considered for the unsaturated model
(\ref{eqn::wald_nus}). The performance of the detector is evaluated using both test-cell and truck data sets.

The saturated model-based detector demonstrates greater reliability compared to the unsaturated model-based detector.
This improved performance can be attributed to the following factors:
\begin{enumerate}
        \item The parameter estimates of the saturated model do not require backward differencing, in contrast to the unsaturated model, which amplifies noise through this process.
        \item The saturated model contains fewer parameters than the unsaturated model, resulting in a less stringent persistence of excitation condition and reducing the risk of overfitting noise.
        \item The parameter estimation method for the saturated model is more robust to cross-sensitivity errors because it utilizes highly selective data for estimation. Only data points near saturation are employed for parameter estimation.
\end{enumerate}
Therefore, the saturated model parameter estimation-based detector represents a logical choice for catalyst aging
detection in SCR-ASC systems.
