\begin{acknowledgments}
    I would like to acknowledge the support of my co-advisors, Professor Bin
    Yao and Professor Peter H. Meckl, for their consistent guidance, insights,
    and feedback throughout my PhD studies. I am thankful to Professor Bin Yao
    for training me in control theory and for his continual encouragement and
    advice, which were instrumental in bringing this research together. I am
    grateful for the opportunity to pursue my PhD under his mentorship.

    I am deeply indebted to Professor Peter H. Meckl for his steadfast
    guidance and inspiration in shaping the SCR-ASC modeling and diagnostic
    research. His support through Research Assistantships during most of my PhD
    made this work possible. I appreciate his consistent and constructive
    feedback, which was essential in developing my thesis research. I am also
    thankful to Professor Meckl for giving me the opportunity to work on the
    Diesel Engine Aftertreatment System project and pursue the research
    presented in this thesis.

    I would like to thank Professor Richard Voyles for providing hardware and
    laboratory support, as well as for assisting in defining a practical and
    meaningful research problem related to the Dexterous Hexrotor, which was my
    initial project during the PhD program. I thank Professor George Chiu for
    his time, review of the work, and valuable suggestions, which enhanced the
    quality and clarity of this thesis. I would also like to thank the School
    of Mechanical Engineering for providing TA support during the initial part
    of my PhD studies.

    I am sincerely grateful to Cummins Inc. for providing the data and
    sponsorship that enabled the SCR-ASC studies. I especially thank David
    Schmidt for his detailed discussions regarding system architectures,
    testing procedures, and truck data, which significantly influenced the
    modeling and diagnostic work. I also appreciate the support, insights, and
    collaboration of Adam Kidd, Larry Brunner, Tom Nelson, and Lyle Kocher
    throughout the project. I would like to acknowledge the foundational
    contributions of Kaushal Kamal Jain, whose earlier work established
    important groundwork for this research.

    Finally, I would like to thank my friends and family, especially my wife
    Shruthi, for their unwavering encouragement, patience, and understanding.
    Their constant support has been invaluable, and this accomplishment would
    not have been possible without them.
\end{acknowledgments}
