\begin{abstract}%
The existing approach to modelling the reaction flows of diesel engine Selective Catalytic Reduction
after-treatment (SCR-ASC) system uses a sequence of Continuously Stirred Tank Reactors (CSTRs) (n-cell models) to
approximate the PDE's that arise from the plug-flow reactions by discretizing in space. This model introduces a
causality reversal in computation of reaction rates in each cell as they become function of outlet concentrations, i.e,
the concentrations of the products after the reaction. This approximation breaks down when the n-cell model is reduced
down to a single-cell in order to have minimal realization of the dynamics. Thus, the CSTR modelling approach requires
multiple cells to appropriately capture the reaction dynamics, increasing the number of states and parameters that need
estimation. Further, it is observed that the sampling time for the measurement signals is larger than the actual
residence time of the reactants in the chamber. Thus, the measurement signals only capture the averaged effects of the
reactions happening in multiple residence times.

Considering these insights, the present work aims to develop a reduced-order nonlinear discrete model from first
principles that can be parametrized into an identifiable model. Instead of discretizing the plug-flow reaction in space,
we first discretize the system in time considering the interplay between the residence time and sampling time. Then the
reaction process dynamics in the SCR chamber is lumped and reduced to a few significant reactions whose effect on
the time evolution of the measurement signals at the inlet and outlet of the chamber is modelled as a set of difference
equations based on the molar conservation of species. These equations are parametrized as the function of inputs and
states using approximate models for physical properties such as rate constant and density based on the operating
conditions of the system. Finally, an identifiable model for the $NO_x$ process dynamics is developed and validated with
the test-cell data.

Further, the model parameters are shown to be sensitive to the catalyst's aging state. Using the paramter estimates and
their statistics, a hypothesis-testing framework based on the Wald test is developed to detect catalyst aging.
The performance of the proposed aging detector is demonstrated using both test-cell data at different aging
levels and real-world data from four long-haul trucks.
\end{abstract}
