\chapter{Data Characteristics}
A critical criterion for assessing the validity of a developed model or diagnostic algorithm is its performance on real-world data, whether sourced from controlled experiments or operational vehicles. For this study, Cummins supplied both test-cell and truck data. Test-cell data were obtained by operating the test cell using established standard drive cycles. Truck data were collected from four long-haul trucks over a one-day period, first with fresh (degreened) catalysts and later after catalyst aging.
%===============================================================================
\input{./secs/2-data/0-subs/0-1_test_cell_data.tex}
%===============================================================================
\input{./secs/2-data/0-subs/0-2_truck_data.tex}
% ===============================================================================



The available test and truck data for testing the model structure needs to be put into common units. The following table
lists the units used for each of the physical properties.
\begin{table}[H]
   \centering
   \begin{tabular}{l l}
       \hline \hline
        \itbf{Property} & \itbf{Unit}\\
        \hline \hline
        Concentration   & $ 10^{-3} \, mol/m^{3}$ \\
        Temperature     & $ \times 10 + 200\lx{^o}{C}$ \\
        Flow Rate   & $\times 10 \, g/s$ \\
        Urea Injection  & $\times 10^{-1}\, ml/s$ \\
        Time            & $s$ \\
        \hline \hline
   \end{tabular}
   \caption{Table of Units used in the Model}
\end{table}

The available data and corresponding units are listed in the following table.

% ==============================================================================
\input{./secs/2-data/1-density.tex}
\input{./secs/2-data/2-ppm.tex}
\input{./secs/2-data/3-flow_rate.tex}
% ==============================================================================

\section{Test-Cell Data Preprocessing}
% \input{./secs/2-data/tst_filt/sig_ranges.tex}

%==============================================================================

% \subsection{Signal Processing Steps}
\input{./secs/2-data/pipeline.tex}

% ==============================================================================

\section{Truck Data Preprocessing}
% \input{./secs/2-data/trk_filt/sig_ranges.tex}

% =============================================================================

% \subsection{Signal Processing Steps}
The road data was collected from trucks operating in the United States  for two days separated by a few years
(Table~\ref{tab::truck_data_summary}) during which the catalyst has aged based on the existing performance measures. The
data contains measurements of $NO_x$ sensors before and after the catalyst, as well as other required variables
including flow rate, temperature and urea injection rate. The data preporcessing includes,
\begin{enumerate}
        \item removing the rows with missing values,
        \item removing the rows whose operating temperature range is beyond range of $200-300 \,^0C$,
        \item interpolating the missing data if the data breaks are smaller than a minute, and finally,
        \item smooting the data using non-causal chebyshev filter.
\end{enumerate}
The preprocessed data is than partitioned into drive segments with no breaks which correspond to a continuous driving
period from engine start to engine stop.
%===
\begin{table}[H]
        \centering
        \caption{Truck Data Set Years and Mileage Difference}
        \label{tab::truck_data_summary}
        \begin{tabular}{l l l r}
        \hline \hline
               & Earlier Data & Latter Data & Milage \\
         Truck &  Year            & Year    & Difference\\ \hline \hline
        AD Transport (adt) & $2015$ & $2017$ & $2.79 \times 10^5$\\
        Mesilla Valley (mes) & $2015$ & $2018$ & $11.87 \times 10^5$\\
        Werner (wer) & $2015$ & $2017$ & $5.89 \times 10^5$\\
        Transwest (trw) & $2015$ & $2016$ & $6.56 \times 10^5$ \\
        \hline \hline
        \end{tabular}
\end{table}


% ==============================================================================
\input{./secs/2-data/n-res_time.tex}
\input{secs/5-sat_detect/paper/2-subs/2-4-NOx_crosssensitivity.tex}
